Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-03 main.tex
Related work

>>>>

\item Hritcu et al's work on ``Testing Noninterference
Quickly''~\cite{DBLP:journals/jfp/HritcuLSADHPV16} laid the
foundation of the random testing strategy that we use here.  In particular,
that paper explored testing strategies based on both standard ``End-to-end
noninterference''---a pleasantly extensional and easy-to-define property
that leads to somewhat inefficient testing because process that misbehaves
while its PC is labeled ``high'' must return to a low PC before the
misbehavior can be identified as such---and ``Single-step
noninterference''---a more intricate property related to Goguen and
Meseguer's ``unwinding conditions''~\cite{GoguenMeseguer85} that ``fails
faster'' and is thus easier to test.  \bcp{Explain the relation of the
  latter property to our stack testing strategy.}
